---
title: "Police Brutality Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
```

## Introduction
The police in the United Stated have been abusing their power and responsibilities to serve us. Instead year after year, we hear that people are being killed by them and it tends to be people of color specifically blacks. We decided to look into three datasets, the first being [police brutality]("https://raw.githubusercontent.com/info201b-au20/info201finalGEKK/gh-pages/2013-2020%20Police%20Killings-Table%201.csv"), the second one [killings by police department]("https://raw.githubusercontent.com/info201b-au20/info201finalGEKK/gh-pages/2013-2019%20Killings%20by%20PD-Table%201.csv"), and lastly [killings by state]("https://raw.githubusercontent.com/info201b-au20/info201finalGEKK/gh-pages/2013-2019%20Killings%20by%20State-Table%201.csv"). With these we will find out the deaths per year, races targeted, and locations it happened.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
chart1
chart2
print("To be able to get a visual of the growth or decrease in the past decade, we grabbed all the deaths in a given year and sorted it out. In the line graph below we can see that since 2013 there have been a consistent amount of deaths by police reaching over 1000. We noticed that in 2020 there were the least amount but take into consideration that the year is not over.")
plot(a, type="o",
     col = "blue",
     main = "police brutality: YEAR vs. DEATHS", 
     xlab = "Year",
     ylab = "Deaths by Cops")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

